---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CausalArima

<!-- badges: start -->
<!-- badges: end -->

The goal of CausalArima is to estimates the causal effect of an intervention on a univariate time series using ARIMA models.

## Installation

<!-- You can install the released version of CausalArima from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("CausalArima") -->
<!-- ``` -->

You can install the development version of CausalArima from from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FMenchetti/CausalArima")
```
## Example

This is a basic example which shows you how to use the package:

```{r example, warning=FALSE, }
library(CausalArima)

# simulate data
n<-100
set.seed(1)
x1 <- 100 + arima.sim(model = list(ar = 0.999), n = n)
y <- 1.2 * x1 + rnorm(n)
y[ floor(n*.71):n] <- y[ floor(n*.71):n] + 10
data <- cbind(y, x1)
dates <- seq.Date(from = as.Date("2014-01-05"), by = "days", length.out = n)
start<-as.numeric(strftime(as.Date(dates[1], "%Y-%m-%d"), "%u"))

# Adding a fictional intervention
int.date <- as.Date("2014-03-161")

# fit the model - Causal effect estimation
ce <- CausalArima(y = ts(y, start = start, frequency = 1), auto = TRUE, ic = "aicc", dates = dates, int.date = int.date,
                  xreg =x1)
```



```{r, warning=FALSE, message=FALSE}
fore<-plot(ce, type="forecast")
impact<-plot(ce, type="impact")
table(ce)
```


```{r}
residuals<-plot(ce, type="residuals")
```



You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
