---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CausalArima

<!-- badges: start -->
<!-- badges: end -->

The goal of CausalArima is to estimates the causal effect of an intervention on a univariate time series using ARIMA models.

## Installation

<!-- You can install the released version of CausalArima from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("CausalArima") -->
<!-- ``` -->

You can install the development version of CausalArima from from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FMenchetti/CausalArima")
```
## Example

This is a basic example which shows you how to use the package:

```{r example, warning=FALSE, }
library(CausalArima)

# simulate data
n<-100
set.seed(1)
x1 <- 100 + arima.sim(model = list(ar = 0.999), n = n)
y <- 1.2 * x1 + rnorm(n)
y[ floor(n*.71):n] <- y[ floor(n*.71):n] + 10
data <- cbind(y, x1)
dates <- seq.Date(from = as.Date("2014-01-05"), by = "days", length.out = n)
start<-as.numeric(strftime(as.Date(dates[1], "%Y-%m-%d"), "%u"))

# Adding a fictional intervention
int.date <- as.Date("2014-03-161")

# fit the model - Causal effect estimation
ce <- CausalArima(y = ts(y, start = start, frequency = 1), auto = TRUE, ic = "aicc", dates = dates, int.date = int.date,
                  xreg =x1)
```

How to obtain the plot of the forecast:

```{r, warning=FALSE, message=FALSE}
forecasted<-plot(ce, type="forecast", printing=FALSE)
forecasted
```

How to obtain the plot of the estimated effects and cumulative effects:
```{r}

impact<-plot(ce, type="impact", printing=FALSE)
grid.arrange(impact$plot, impact$cumulative_plot)
```

How to obtain the estimates of the effects:
```{r}
print(ce)
table(ce)
```

How to inspect the residuals, with the plots of autocorrelation (ACF) and partial autocorrelation (PACF) functions and QQ-plots:
```{r}
residuals<-plot(ce, type="residuals", printing=FALSE)
grid.arrange(residuals$ACF, residuals$PACF, residuals$QQ_plot)
```


## Learn more

You can read more on [Estimating the causal effect of an intervention in a time series setting: the C-ARIMA approach
](https://arxiv.org/abs/2103.06740) (Fiammetta Menchetti, Fabrizio Cipollini, Fabrizia Mealli, 2021).

It is also available on youtube a video of a webinar on the topic:
[Fiammetta Menchetti: Estimating the causal effect of an intervention in a time series setting](https://www.youtube.com/watch?v=RjMEtv3C5S0).




